\bibliographystyle{IEEEtran}
\begin{thebibliography}{14}
\bibitem{1} V. Tarokh, H. Jafarkhani, and A. R. Calderbank, "Space-time block codes from orthogonal designs," \textit{IEEE Trans. Inf. Theory}, vol. 45, no. 5, pp. 1456-1467, Jul. 1999.

\bibitem{2} L. Zheng and D. N. C. Tse, "Diversity and multiplexing: A fundamental tradeoff in multiple-antenna channels," \textit{IEEE Trans. Inf. Theory}, vol. 49, no. 5, pp. 1073-1096, May 2003.

\bibitem{3} B. A. Sethuraman, B. Sundar Rajan, and V. Shashidhar, "Full-diversity, high-rate space-time block codes from division algebras," \textit{IEEE Trans. Inf. Theory}, vol. 49, no. 10, pp. 2596-2616, Oct. 2003.

\bibitem{4} V. Tarokh, N. Seshadri, and A. R. Calderbank, "Space-time codes for high data rate wireless communication: performance criterion and code construction," \textit{IEEE Trans. Inf. Theory}, vol. 44, no. 2, pp. 744-765, Mar. 1998.

\bibitem{5} S. M. Alamouti, "A simple transmit diversity technique for wireless communications," \textit{IEEE J. Sel. Areas Commun.}, vol. 16, no. 8, pp. 1451-1458, Oct. 1998.

\bibitem{6} J.-C. Belfiore, G. Rekaya, and E. Viterbo, "The Golden code: a 2x2 full-rate space-time code with nonvanishing determinants," \textit{IEEE Trans. Inf. Theory}, vol. 51, no. 4, pp. 1432-1436, Apr. 2005.

\bibitem{7} F. Oggier, G. Rekaya, J.-C. Belfiore, and E. Viterbo, "Perfect space-time block codes," \textit{IEEE Trans. Inf. Theory}, vol. 52, no. 9, pp. 3885-3902, Sep. 2006.

\bibitem{8} P. Elia, K. R. Kumar, S. A. Pawar, P. V. Kumar, and H.-F. Lu, "Explicit space-time codes achieving the diversity-multiplexing gain tradeoff," \textit{IEEE Trans. Inf. Theory}, vol. 52, no. 9, pp. 3869-3884, Sep. 2006.

\bibitem{9} K. P. Srinath and B. S. Rajan, "Low ML-decoding complexity, large coding gain, full-rate, full-diversity STBCs for 2×2 and 4×4 MIMO systems," \textit{IEEE J. Sel. Topics Signal Process.}, vol. 3, no. 6, pp. 916-927, Dec. 2009.

\bibitem{10} S. Sezginer and P. Schniter, "A comprehensive overview of division-algebra-based space-time codes," \textit{Foundations and Trends in Communications and Information Theory}, vol. 10, no. 3-4, pp. 191-324, 2014.

\bibitem{11} M. O. Damen, H. El Gamal, and G. Caire, "On maximum-likelihood detection and the search for the closest lattice point," \textit{IEEE Trans. Inf. Theory}, vol. 49, no. 10, pp. 2389-2402, Oct. 2003.

\bibitem{12} B. Hassibi and H. Vikalo, "On the sphere-decoding algorithm I. Expected complexity," \textit{IEEE Trans. Signal Process.}, vol. 53, no. 8, pp. 2806-2818, Aug. 2005.

\bibitem{13} H. Yao and G. W. Wornell, "Achieving the full MIMO diversity-multiplexing frontier with rotation-based space-time codes," \textit{Proc. 41st Allerton Conf. Communication, Control, and Computing}, Monticello, IL, Oct. 2003.

\bibitem{14} G. J. Foschini et al., "Simplified processing for high spectral efficiency wireless communication employing multi-element arrays," \textit{IEEE J. Sel. Areas Commun.}, vol. 17, no. 11, pp. 1841-1852, Nov. 1999.
\end{thebibliography}
